smdi: An R package to perform structural missing data investigations on partially observed confounders in real-world databases

### 2023-07-31 manuscript/manuscript.qmd
minor formatting changes

[**Word count:**]{.underline} xxxx words

[**Tables:**]{.underline}

[**Figures:**]{.underline}

@@

[**Analytical code and data sharing statement:**]{.underline} This manuscript was written using `Quarto` version 1.3.433 (<https://quarto.org/>) and R version 4.1.2. All R code and materials can be found at <https://gitlab-scm.partners.org/drugepi/smdi-manuscript>. Detailed information on packages and versions can be found in the `renv.lock` file in the linked repository. The R package and data presented in this study can be downloaded from <https://janickweberpals.gitlab-pages.partners.org/smdi/>.

@@

>>>>

[**Word count:**]{.underline} xxxx words/2000 words

[**Tables:**]{.underline} **x/2**

[**Figures:**]{.underline} **x/3**

@@

[**Analytical code and data sharing statement:**]{.underline} This manuscript was written using `Quarto` version 1.3.433 (<https://quarto.org/>) and R version 4.1.2. All R code, materials and depedency information can be found at <https://gitlab-scm.partners.org/drugepi/smdi-manuscript>. The R package presented in this study can be downloaded from CRAN via `install.packages("smdi")` or from <https://janickweberpals.gitlab-pages.partners.org/smdi/>.

@@

xxx words/150 words
